---
title: 'hw01: Set-up'
author: | 
  | Your Name^[Email: ]
  | Affiliation
date: '`r format(Sys.time(), "%Y/%m/%d")`'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    includes:
      in_header: asset/latex/custom.sty
    keep_tex: no
    latex_engine: pdflatex
    number_sections: yes
    template: null
    toc: no
  bookdown::html_document2: default
documentclass: scrartcl
link-citations: yes
bibliography: asset/bib/packages.bib
biblio-style: apalike
---

# Example: R code and output in a document

```{r}
library(tidyverse)
(iris_tbl <- as_data_frame(iris))
```

The raw output of R is not very beautiful for PDF. You probably want to use `knitr::kable()` function of **knitr** package [@R-knitr] to print a table. Table \@ref(tab:iris-print) is produced by the following code.

```{r iris-print}
knitr::kable(head(iris_tbl, 10), caption = "Iris dataset")
```

The following code generates and print Figure \@ref(fig:iris).^[See http://stackoverflow.com/questions/38861041/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables/38884378#38884378]

```{r iris, fig.cap="Iris Data", fig.align='center', fig.width=4, fig.height=3}
ggplot(iris_tbl) + 
  geom_point(aes(x = Sepal.Length, y = Petal.Length, color = Species)) 
```


# Example: Mathematical expressions using LaTeX

You can produce mathematical equations using LaTeX syntax: 

\begin{equation}
f(x) = f(0) + \int_0^x f'(y) dy.  (\#eq:ftc)
\end{equation}


Cross reference works like Equation \@ref(eq:ftc) but the syntactic rule is different from LaTeX. 
See [https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#equations](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#equations) for more detail.


# References {-}


